We work with SD--JWT credentials, extensions to other formats are straightforward. The construction adds a zero-knowledge layer around the issued credential and is instantiated with Spartan as the proof system and Hyrax-style Pedersen vector commitments; standard zero-knowledge blinding is applied.

\paragraph{Objects and notation.}
Let $S$ be the issued credential with messages $(m_1,\dots,m_N)$, per-message salts $(s_1,\dots,s_N)$, hashes $(h_1,\dots,h_N)$, and issuer signature $\sigma_I$ under public key $PK_I$. The wallet public key $PK_W$ is included among the messages. A presentation policy is modeled as predicates $f_1,\dots,f_K$ over $(m_i)$.

\paragraph{Two relations.}
Proving is split into two relations with a fixed interface:
\begin{itemize}[leftmargin=1.2em]
  \item Prepare: Once per credential, prove the correct parsing of $S$, that $h_i=\mathrm{SHA256}(m_i,s_i)$ for all $i$, that $\mathrm{Verify}(\sigma_I,PK_I)=1$, and compute a Hyrax commitment $C_m$ to the \emph{message vector} $(m_i)$. This relation is independent of the presentation policy; its proof can be re-randomized and reused.
  \item Show: For a given policy, prove that each requested predicate $f_j(m_1,\dots,m_N)$ holds and that a live signature on the verifier’s challenge verifies under the wallet public key bound in $S$. Publish a commitment $C'_m$ to the same message vector.
\end{itemize}
The link is enforced by checking $C_m=C'_m$ (Hyrax commitment equality), so no auxiliary link primitive is required. Because equality is checked in one group, both relations use the same curve.

\paragraph{Workflow.}
Issuance produces $S$ and binds it to $PK_W$. At presentation, the verifier sends a fresh challenge $\mathsf{nonce}_V$; the wallet signs $\mathsf{nonce}_V$ with the corresponding secret key and returns $(\pi_{\texttt{prepare}},\pi_{\texttt{show}})$. The verifier validates both proofs and accepts only if $C_m=C'_m$.

\paragraph{Security note.}
Hyrax commitments rely on discrete-log hardness; this instantiation is not post-quantum. A lattice-based commitment can replace Hyrax to obtain a post-quantum variant without changing the interface of the two relations.
